A novell interest management algorithm for distributed simulations of MMGs

### 2008-04-30 trunk/textos/dsrt/engaoi.tex
eng

Os resultados foram coletados da seguinte maneira: para encontrar a largura de banda utilizada em média para envio, foram somados todos os pacotes de cada sessão e dividido pelo tempo que foi simulado; para determinar a largura de banda máxima utilizada, foi verificado, segundo a segundo, quantos bytes foram enviados e foi selecionado o máximo.

Nas tabelas \ref{tab_max} e \ref{tab_avg}, são apresentados os dados coletados de largura de banda máxima e média, respectivamente, utilizada com os quatro algoritmos simuladas - área em círculo (\circleaoi), área em círculo com atenuação (\circleat), área do campo de visão (\fov) e área do campo de visão mais área próxima mais atenuação (\malg) - além de mostrar quanto seria a largura de banda utilizada se nenhuma técnica fosse empregada (\noaoi). Os valores estão em bytes/s. Nas figuras \ref{fig_max} e \ref{fig_avg} são mostrados os gráficos correspondentes.

>>>>

The results were collected as follows: to measure the average upload bandwidth usage by the server, the sizes of all packets sent in the session were summed up and then divided by the session duration; to determine the maximum bandwidth usage by the server, it was measured, second by second, how many bytes had been sent and the highest value was selected.

In tables \ref{tab_max} and \ref{tab_avg}, the collected maximum and average upload bandwidth usage data are presented for each number of simulated avatars and interest management algorithm - circular area based (\circleaoi), circular area based with attenuated update frequency (\circleat), field of view based (\fov) and \malg\ algorithm - and it is also show how much would be the upload bandwidth usage if no technique at all was employed (\noaoi). The values presented are in bytes per second. In Figure \ref{fig_max} and Figure \ref{fig_avg}, the corresponding graphics are given.
